\documentclass{article}

\usepackage{geometry}[margin=1in]

\begin{document}
Mode Bit: 0 / 1 (kernel / user)

\textbf{DMA} Direct Memory Access

Does direct addressing of memory imply that the O.S is not involved?

\section*{An OS is a program that runs other programs.}
Where is the source code?

\begin{itemize}
    \item \textbf{Multprogramming} increases CPU utilization by ensuring the CPU always has something to execute
    \item Several jobs are kept in memory
    \item Memory Hierarchy (not all jobs can be `in' memory at one time)
    \item Hence the use of a job pool!
    \item OS picks one of the jobs in memory to execute.
    \item When a job is waiting for an I/O Operation, OS switches to another job
    \item Security
\end{itemize}

\textbf{If several jobs are kept in memory, does that mean all of them are running at the same time?}
No!

\textbf{What security vulnerabilities should we prevent?}
If we have job 2 as Skype and job 4 as firefox, skype shouldn't be able to access the memory that firefox uses.

The OS handles \underline{where} application data is placed when being moved
in/out of memory, cache, etc, and where the evicted data needs to go.

Three ways that programs invoke system calls
\begin{itemize}
    \item GUI: Graphical User Interface
    \item batch: scripting
    \item Command Line
\end{itemize}

OS thus needs to provide:
\begin{description}
    \item[Program Execution:] Load program into memory and run item
    \item[I/O operations:] Send data to screen, speaker, to/from file, etc.
    \item[File systems:] Create, delete, add to file, etc.
\end{description}

\textbf{How would one process communicate with another?}
\begin{itemize}
    \item Shared Memory
    \item Message passing (semaphores)
\end{itemize}

These services do not necessarily guarantee fair use of resources.

\begin{itemize}
    \item \textbf{Resource Allocation}
          \begin{itemize}
              \item Scheduling algorithms
          \end{itemize}
    \item \textbf{Accounting}
          \begin{itemize}
              \item Which user/process uses how much of a specific resource
              \item VM is \textit{basically} accounting
              \item Programs need time, space, and fair access.
          \end{itemize}
    \item \textbf{Protection and Security}
          \begin{itemize}
              \item Make sure data from one process/user is not accessible to another process/user
          \end{itemize}
\end{itemize}

The command interpreter has no knowledge of what a command does, but instead launches a system program

Located in \texttt{usr/include/x86\_64-linux-gnu/sys}

\textbf{How are parameters passed to the OS?}
\begin{enumerate}
    \item Registers
    \item Save parameters in block or table (memory) and pass via a register
\end{enumerate}
\end{document}